### 2009-04-20 doc/a-rex/arex_tech_doc.tex
Documented extra lines in job.ID.local and extra config lines

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration (This feature
does not work in current implementation).
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persists if the termination of the previous 
job fails.
\end{itemize}
\end{itemize}

@@

>>>>

\begin{itemize}
\item \textit{subject} -- user certificate's subject, also known as the distinguished
name (DN)
\item \textit{starttime} -- GMT time when the job was accepted represented
in the Generalized Time format of LDAP 
\item \textit{lifetime} -- time period to preserve the SD after the job has
finished in seconds
\item \textit{cleanuptime} -- GMT time when the job should be removed from
the cluster and it's SD deleted in Generalized Time format
\item \textit{notify} -- email addresses and flags to send mail to about
the job specified status changes
\item \textit{processtime} -- GMT time when to start processing the job in
Generalized Time format
\item \textit{exectime} -- GMT time when to start job execution in Generalized
Time format
\item \textit{expiretime} -- GMT time when the credentials delegated to the
job expire in Generalized Time format
\item \textit{rerun} -- number of retries left to rerun the job
\item \textit{jobname} -- name of the job as supplied by the user
\item \textit{projectname} -- name of the project as supplied by the user
\item \textit{lrms} -- name of the LRMS backend to be used for local submission
\item \textit{queue} -- name of the queue to run the job at
\item \textit{localid} -- job id in LRMS (appears only after the job has
reached state \textbf{InLRMS})
\item \textit{globalid} -- BES ActivityIdentifier XML tree, the global
identifier of the job
\item \textit{args} -- executable name followed by a list of command-line
arguments
\item \textit{downloads} -- number of files to download into the SD before
execution
\item \textit{uploads} -- number of files to upload from the SD after execution
\item \textit{gmlog} -- directory name which holds files containing information
about the job when accessed through GridFTP interface
\item \textit{clientname} -- name (as provided by the user interface) and
IP address:port of the submitting client machine
\item \textit{clientsoftware} -- version of software used to submit the job
\item \textit{sessiondir} -- the job's SD
\item \textit{failedstate} -- state in which job failed (available only if
it is possible to restart the job)
\item \textit{jobreport} -- URL of a user requested \emph{logger service}.
The A-REX will also send job records to this service in addition to
the default logger service configured in the configuration.
\item \textit{activityid} -- Job-id of previous job in case the job has been 
resubmitted or migrated. This value can appear multiple times if a job has been 
resubmitted or migrate more than once.
\item \textit{forcemigration} -- This boolean is only used for migration of jobs.
It determines whether the job should persists if the termination of the previous 
job fails.
\end{itemize}
\end{itemize}

@@

\item \textbf{\textit{jobreport\_credentials}}\textit{={[}key\_file
    {[}cert\_file {[}ca\_dir]]]} -- specifies the credentials for
  accessing the authentication service.
\item \textbf{\textit{jobreport\_options}}\textit{={[}options]}
  -- specifies additional options for Usage Reporter and/or
  accounting service. The \textit{options} string is interpreted by Usage
  Reporter, its format is described in the corresponding technical document.
